Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-08 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{prot_teff_Santos19_Santos21_dquality.pdf}
		}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{koi_mean_prot_teff_koi_X_S19S21dquality_keepgrazing.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Rotation periods for Kepler target stars (left) and known
			planet hosts (right)}.  
		The gray lines are ``mean fits'' 
		to the slow rotation sequences of M67,
		Ruprecht~147, NGC~6811, Praesepe, and a trio of 120\,Myr open
		clusters.  The stellar sample includes only apparently single stars
		near the main sequence with $\log g$$>$4.2, RUWE$<$1.4,
		and 3800$<$$T_{\rm eff}$/K$<$6200.  The displayed planet-hosts require
		the same stellar cuts, and include only the confirmed and candidate planets
		described in Section~\ref{subsec:plflags}.
		An order of magnitude estimate for the number of young planets discovered
		by Kepler follows by counting planets below the mean rotational isochrones.
	}
	\label{fig:prot_vs_teff}
\end{figure*}

@@

\subsubsection{New Young Systems}
%
%The astrophysical processes behind rotation and lithium evolution are
%independent.
%Therefore 
%whenever the two age indicators agree within a
%narrowly-constrained range, confidence in the true age
%increases.
%The region of greatest overlap between rotation and lithium ages is
%dictated by the timescale for lithium depletion: for stars with
%temperatures between 4500-5500\,K with ages $\lesssim$1\,Gyr, we can
%hope to obtain independent two-sided constraints
%\citep{Bouma_2023,Jeffries_2023}.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{prot_teff_Santos19_Santos21_dquality.pdf}
		}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{koi_mean_prot_teff_koi_X_S19S21dquality_keepgrazing.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Rotation periods for Kepler target stars (left) and known
			planet hosts (right)}.  
		The gray lines are ``mean fits'' 
		to the slow rotation sequences of open
		clusters.  The stellar sample (left) includes only apparently single stars
		near the main sequence with $\log g$$>$4.2, RUWE$<$1.4,
		and 3800$<$$T_{\rm eff}$/K$<$6200.
		The color map has a linear stretch.  %between one and ten stars per bin.
		The planet-hosts (right) require
		the same stellar cuts, and include only the confirmed and candidate planets
		described in Section~\ref{subsec:plflags}.
		An order of magnitude estimate for the number of young planets discovered
		by Kepler follows by counting planets below the mean rotational isochrones.
	}
	\label{fig:prot_vs_teff}
\end{figure*}

@@

\subsubsection{New Young Planets}
%
%The astrophysical processes behind rotation and lithium evolution are
%independent.
%Therefore 
%whenever the two age indicators agree within a
%narrowly-constrained range, confidence in the true age
%increases.
%The region of greatest overlap between rotation and lithium ages is
%dictated by the timescale for lithium depletion: for stars with
%temperatures between 4500-5500\,K with ages $\lesssim$1\,Gyr, we can
%hope to obtain independent two-sided constraints
%\citep{Bouma_2023,Jeffries_2023}.
